---
title: "Title: Cooling benefits and forest structure similar across parks with varied land use histories"
format:
  pdf:
    fig-width: 12
    fig-height: 14
knitr:
  opts_knit:
    root.dir: "C:/Users/I_RICHMO/Documents/Repositories/park-legacies"
---

Authors: Isabella C. Richmond^1^\*, Michael A. Paulauskas^1^, Erica Padvaiskas^1^, Laura Carolina Gonzalez Sinisterra^2^, Kayleigh Hutt-Taylor^1^, Alec L. Robitaille^3^, Carly D. Ziter^1^

1 Department of Biology, Concordia University, Montreal Canada, H4B 1R6\
2 Department of Biology, Universidad del Valle, Cali Columbia, 760042 3 Department of Biology, Memorial University of Newfoundland, St John's Canada, A1C 5S7

\* isabella.richmond\@mail.concordia.ca, 438-439-8064

```{r, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
source('R/packages.R')


tar_load(trees_clean)
```

```{r, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
# calculate proportion of buckthorn 

largebuck <- trees_clean %>% 
  group_by(PastLandUse) %>% 
  filter(DBHCalc >= 5) %>% 
  summarize(total = n(),
            notbuck = sum(SpCode != 'RHCA'),
            buckthorn = sum(SpCode == 'RHCA'),
            propbuck = buckthorn/total,
            propnotbuck = notbuck/total,
            treesize = 'Trees >= 5 cm DBH')

smallbuck <- trees_clean %>% 
  group_by(PastLandUse) %>% 
  filter(DBHCalc < 5) %>% 
  summarize(total = n(),
            notbuck = sum(SpCode != 'RHCA'),
            buckthorn = sum(SpCode == 'RHCA'),
            propbuck = buckthorn/total,
            propnotbuck = notbuck/total,
            treesize = 'Trees < 5 cm DBH')

buck <- rbind(largebuck, smallbuck) %>% 
  pivot_longer(cols = c(propbuck, propnotbuck), values_to = 'prop')


ggplot(buck, aes(fill=name, y=prop, x=PastLandUse)) + 
  geom_bar(position='stack', stat = 'identity') + 
  theme_classic() + 
  scale_fill_manual(values = c("#c2d6a4", "#1e3d14"), labels = c("Buckthorn", "Other Species")) +
  labs(x = "", fill = "", y = "% of Total Trees") + 
  facet_wrap(~ treesize)

```

Figure S7. Proportion of common buckthorn (*Rhamnus cathartica*) across past land-use types for trees < 5 cm DBH and trees >= 5 cm DBH. Proportions were calculated across all plots and parks. All other species observed were pooled for the "Other Species" category.