---
title: "Supplementary Figure S3"
format: 
  html:
    toc: true
    html-math-method: katex
    self-contained-math: true
    self-contained: true
knitr:
  opts_knit:
    root.dir: "C:/Users/I_RICHMO/Documents/Repositories/park-legacies"
---

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
source('R/packages.R')
```

## Model Equations
Below are the math stats notations, as well as the `brms` notations, for all models run in our paper. Importantly, we denote the relative cooling effect as: 

$$
({T ^{control}_i} - {T ^{park}_i}) - \overline{(T ^{control} - T ^{park})}
$$

It is important to note that in this notation, $T^{park}_i$, indicates the temperature averaged across all sensors and times for that date (split into daytime or nighttime). Similarly, $T^{control}_i$ indicates the average temperature for the control sensor, averaged across all times for that date (split into daytime or nighttime). $\overline{(T ^{control} - T^{park})}$ indicates the average of all temperature differences, taken across dates and sites.


## Total Effect of Past Land-Use on Cooling Effect

### Model equation:

$$
({T ^{control}_i} - {T ^{park}_i}) - \overline{(T ^{control} - T ^{park})} \sim Normal(\mu_i, \sigma) 
\\
\mu_i = {\bar\alpha + \alpha_{Park[i]} + \alpha_{tod[i]} + \beta _{PastLandUse} *PastLandUse + \beta _{age} *Age}
\\
\bar\alpha \sim Normal(0, 0.5)
\\
\alpha_{Park} ~\sim Normal(0, \sigma_{Park})
\\
\alpha_{tod} ~\sim Normal(0, \sigma_{tod})
\\
\beta_{PastLandUse} \sim Normal(0, 0.5)
\\
\beta_{Age} \sim Normal(0, 0.5)
\\
\sigma_{Park}\sim HalfNormal(0, 0.2)
\\
\sigma_{tod}\sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_5_brms_formula)
```

Where:

-   cooling_s = relative cooling effect (scaled)

-   PastLandUse = past land use category

-   Age_s = age of park (scaled)

-   tod = time of day (daytime or nighttime)

-   Park = park where measurements were taken


## Direct Effect of Past Land-Use on Forest Composition

### Model equation

$$
log(DensL_i) \sim Normal(\alpha, \sigma)
\\
\mu_i = \bar\alpha + \alpha_{PastLandUse[i]}
\\
\bar\alpha\sim Normal(-1.5 ,2)
\\
\alpha_{PastLandUse} \sim Normal(0, \sigma_{PastLandUse})
\\
\sigma_{PastLandUse} \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_2_L_brms_formula)
```

Where:

-   Dens_L_log = density of large trees (logged)

-   PastLandUse = past land use category

### Model equation

$$
log(DensS_i) \sim Normal(\alpha, \sigma)
\\
\mu_i = \bar\alpha + \alpha_{PastLandUse[i]}
\\
\bar\alpha\sim Normal(-1 ,5)
\\
\alpha_{PastLandUse} \sim Normal(0, \sigma_{PastLandUse})
\\
\sigma_{PastLandUse} \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_2_S_brms_formula)
```

Where:

-   Dens_S_log = density of small trees (logged)

-   PastLandUse = past land use category

### Model equation

$$
log(SizeL_i) \sim Normal(\alpha, \sigma)
\\
\mu_i = \bar\alpha + \alpha_{PastLandUse[i]}
\\
\bar\alpha\sim Normal(2.5 , 1)
\\
\alpha_{PastLandUse} \sim Normal(0, \sigma_{PastLandUse})
\\
\sigma_{PastLandUse} \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_3_L_brms_formula)
```

Where:

-   DBH_med_L_log = size of large trees (logged)

-   PastLandUse = past land use category


### Model equation

$$
log(SizeS_i) \sim Normal(\alpha, \sigma)
\\
\mu_i = \bar\alpha + \alpha_{PastLandUse[i]}
\\
\bar\alpha\sim Normal(1, 0.5)
\\
\alpha_{PastLandUse} \sim Normal(0, \sigma_{PastLandUse})
\\
\sigma_{PastLandUse} \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_3_S_brms_formula)
```

Where:

-   DBH_med_L_log = size of small trees (logged)

-   PastLandUse = past land use category

### Model equation

$$
log(RichnessL_i) \sim Normal(\alpha, \sigma)
\\
\mu_i = \bar\alpha + \alpha_{PastLandUse[i]}
\\
\bar\alpha\sim Normal(2, 1)
\\
\alpha_{PastLandUse} \sim Normal(0, \sigma_{PastLandUse})
\\
\sigma_{PastLandUse} \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_4_L_brms_formula)
```

Where:

-   SR_L_log = species richness of large trees (logged)

-   PastLandUse = past land use category


## Direct Effect of Forest Composition on Cooling Effect

### Model equation

::: {style="overflow-x:auto;overflow-y:hidden;"}
$$
({T ^{control}_i} - {T ^{park}_i}) - \overline{(T ^{control} - T ^{park})} \sim Normal(\mu_i, \sigma) 
\\
\mu_i = {\bar\alpha + \alpha_{Park[i]} + \alpha_{tod[i]} + \beta {densL} *densityL + \beta _{sizeL} *sizeL + \beta _{richnessL} *richnessL + \beta _{densS} *densityS + \beta _{sizeS} *sizeS}
\\
\bar\alpha \sim Normal(0, 0.5)
\\
\alpha_{Park} ~\sim Normal(0, \sigma_{Park})
\\
\alpha_{tod} ~\sim Normal(0, \sigma_{tod})
\\
\beta_{densL} \sim Normal(0, 0.5)
\\
\beta_{sizeL} \sim Normal(0, 0.5)
\\
\beta_{richnessL} \sim Normal(0, 0.5)
\\
\beta_{densS} \sim Normal(0, 0.5)
\\
\beta_{sizeS} \sim Normal(0, 0.5)
\\
\sigma_{Park}\sim HalfNormal(0, 0.2)
\\
\sigma_{tod}\sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$
:::
### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_1_brms_formula)
```

Where:

-   cooling_s = relative cooling effect (scaled)

-   Dens_L_s = large tree density (scaled)

-   DBH_med_L_s = large tree size (scaled)

-   SR_L_s = large tree species richness (scaled)

-   Dens_S_s = small tree density (scaled)

-   DBH_med_S_s = small tree size (scaled)

-   tod = time of day (daytime or nighttime)

-   Park = park where measurements were taken


