---
title: "Supplementary Figure S3 - Model Equations"
format: 
  html:
    toc: true
    html-math-method: katex
    self-contained-math: true
    self-contained: true
knitr:
  opts_knit:
    root.dir: "C:/Users/I_RICHMO/Documents/Repositories/park-legacies"
---

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
source('R/packages.R')
```

## Total Effect of Past Land-Use on Cooling Effect

### Model equation:

$$
(\overline{T _{control[i]}} - \overline{T _{park[i]}}) - \overline{(T _{control} - T _{park})} \sim Normal(\mu_i, \sigma) 
\\
\mu_i = {\alpha_{Park, tod[i]} + \beta _{PastLandUse} *PastLandUse + \beta _{age} *Age}
\\
\alpha_j \sim Normal(\bar\alpha, sd)
\\
\bar\alpha \sim Normal(0, 0.5)
\\
\beta \sim Normal(0, 0.5)
\\
sd \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_5_brms_formula)
```

Where:

-   cooling_s = relative cooling effect (scaled)

-   PastLandUse = past land use category

-   Age_s = age of park (scaled)

-   tod = time of day (daytime or nighttime)

-   Park = park where measurements were taken

### Stan code:

```{r, eval = T, echo = F}
tar_read(model_5_brms_stancode)
```

## Direct Effect of Past Land-Use on Forest Composition

### Model equation

$$
log(DensL_i) \sim Normal(\alpha, \sigma)
\\
\mu_i = \alpha_{PastLandUse[i]}
\\
\alpha_j \sim Normal(\bar\alpha, sd)
\\
\bar\alpha\sim Normal(-1.5 ,2)
\\
sd \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_2_L_brms_formula)
```

Where:

-   Dens_L_log = density of large trees (logged)

-   PastLandUse = past land use category

### Stan code:

```{r, eval = T, echo = F}
tar_read(model_2_L_brms_stancode)
```

### Model equation

\$\$

\$\$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_2_S_brms_formula)
```

Where:

-   Dens_S_log = density of small trees (logged)

-   PastLandUse = past land use category

### Stan code:

```{r, eval = T, echo = F}
tar_read(model_2_S_brms_stancode)
```

### Model equation

\$\$

\$\$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_3_L_brms_formula)
```

Where:

-   DBH_med_L_log = size of large trees (logged)

-   PastLandUse = past land use category

### Stan code:

```{r, eval = T, echo = F}
tar_read(model_3_L_brms_stancode)
```

### Model equation

\$\$

\$\$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_3_S_brms_formula)
```

Where:

-   DBH_med_L_log = size of small trees (logged)

-   PastLandUse = past land use category

### Stan code:

```{r, eval = T, echo = F}
tar_read(model_3_S_brms_stancode)
```

### Model equation

\$\$

\$\$

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_4_L_brms_formula)
```

Where:

-   SR_L_log = species richness of large trees (logged)

-   PastLandUse = past land use category

### Stan code:

```{r, eval = T, echo = F}
tar_read(model_4_L_brms_stancode)
```

## Direct Effect of Forest Composition on Cooling Effect

### Model equation

::: {style="overflow-x:auto;overflow-y:hidden;"}
$$
(\overline{T _{control[i]}} - \overline{T _{park[i]}}) - \overline{(T _{control} - T _{park})} \sim Normal(\mu_i, \sigma)
\\
\mu_i = {\alpha_{Park, tod[i]} + \beta {densL} *densityL + \beta _{sizeL} *sizeL + \beta _{richnessL} *richnessL + \beta _{densS} *densityS + \beta _{sizeS} *sizeS}
\\
\alpha_j \sim Normal(\bar\alpha, sd)
\\
\bar\alpha \sim Normal(0, 0.5)
\\
\beta \sim Normal(0, 0.5)
\\
sd \sim HalfNormal(0, 0.2)
\\
\sigma \sim Exponential(1)
$$
:::

### brms syntax:

```{r, eval = T, echo = F}
tar_read(model_1_brms_formula)
```

Where:

-   cooling_s = relative cooling effect (scaled)

-   Dens_L_s = large tree density (scaled)

-   DBH_med_L_s = large tree size (scaled)

-   SR_L_s = large tree species richness (scaled)

-   Dens_S_s = small tree density (scaled)

-   DBH_med_S_s = small tree size (scaled)

-   tod = time of day (daytime or nighttime)

-   Park = park where measurements were taken

### Stan code:

```{r, eval = T, echo = F}
tar_read(model_1_brms_stancode)
```
